### 2015-11-06 CVPR16/Source/applications.tex
Edit Section 4.1

Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ of the $j$\textsuperscript{th} point track with $i$\textsuperscript{th} object at depth $\lambda$ can be defined as
\begin{align}
\assocP = \Prefl\Ptrans,
\label{eq:defineassocP}
\end{align}
where $\Prefl$ and $\Ptrans$ are from \eqref{eq:evalPrefl} and \eqref{eq:evalCumulativePtrans} respectively. Note that the fraction $\assocP$ although called association probability does not capture the entire information that we have available for computing association of point tracks to objects. This above fraction is the association probability given the hypothesized parameters of objects in the scene.

To compute the association probability $\assocP$ between point track $j$ and object $i$, we must use the reprojection error as well. When the association of $i$ and $j$ is correct and the point of reflection is at depth $\lambda$, the reprojection error must be zero \eqref{eq:reprojerror}, otherwise the error becomes a measure of distance from the true solution. The error term can be converted to probability domain by considering the error term as negative log of probability
\begin{align}
  P^{(ij)}_{\text{assoc by reproj}}(\lambda) = \frac{1}{Z}\exp(-\Ereproj(\lambda))
\end{align}

Using both of the above evidence terms we can write the probability of association $P^{(ij)}_{\text{assoc}}$ as follows
\begin{align}
  P^{(ij)}_{\text{assoc}} = \frac{1}{Z'}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda
  \label{eq:prob-assoc}
\end{align}
Once we have the probability of association $P^{(ij)}_{\text{assoc}}$ we can compute the best possible assignment of object for each point track. The points having very small association probability are assigned to the background,
\begin{align}
  i^*_{j} = \arg \min_{i} \int_0^\infty \assocP \Ereproj(\lambda) d\lambda
\end{align}

>>>>

Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ between point track $j$ and object $i$ at depth $\lambda$ can be defined as
\begin{align}
\assocP = \Prefl\Ptrans,
\label{eq:defineassocP}
\end{align}
where $\Prefl$ and $\Ptrans$ are from \eqref{eq:evalPrefl} and \eqref{eq:evalCumulativePtrans} respectively. Note that the fraction $\assocP$ although called association probability does not capture the entire information that we have available for computing association of point tracks to objects. This above fraction is the association probability given the hypothesized parameters of objects in the scene.

To compute the association probability $\assocP$ between point track $j$ and object $i$, we must use the reprojection error as well. When the association of point track $j$ and object $i$ is correct and the point of reflection is at depth $\lambda$, the reprojection error must be zero \eqref{eq:reprojerror}, otherwise the error becomes a measure of distance from the true solution. The error term can be converted to probability domain by considering the error term as negative log of probability
\begin{align}
  P^{ij}_{\text{assoc by reproj}}(\lambda) = \frac{1}{Z}\exp(-\Ereproj(\lambda))
\end{align}

Using both of the above evidence terms we can define the new association probability $P^{ij}_{\text{assoc}}$ as follows
\begin{align}
  P^{ij}_{\text{assoc}} = \frac{1}{Z'}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda
  \label{eq:prob-assoc}
\end{align}
Once we have the association probability $P^{ij}_{\text{assoc}}$ we can compute the best possible assignment of object for each point track. The points having very small association probabilities are assigned to the background.
